Anonymous provision of services via blockchain

### 2021-12-29 main.tex
update problem statement refer to literature

\begin{abstract}
Lorem ipsum\ldots
\end{abstract}
\keywords{data privacy, zk-SNARK, blockchain}

\section{Problem statement}
Service providers (SP) like: lawyers, laboratories, auditors, or banks, to provide services, require data that is often associated with user identity. The guarantee of the privacy of the data is based on a trust assumptions and security of IT systems. However, most of the service providers don't need the information of user identity for other reasons than payment, communication, or logistics. It would be desirable if the user could keep its identity private, while service provider still provide its services. This could lead to reduced trust that users have to put on SP and less responsibility borne by SP.

In this paper we propose a protocol for anonymous provision of services via blockchain and cryptography. Specificaly, we use
\begin{enumerate}
    \item \textbf{confidential blockchain} to process payment for a service without revealing a user's identity.
    \item \textbf{zero-knowledge proofs} — to proof the payment for the service without revealing the payment itself.
    \item \textbf{encryption scheme and blockchain} — to asynchronously deliver the results of the made service back to the user.
\end{enumerate}

@@

\section{Applications}
\subsections{Clinical tests}
Bodybuilders, athletes,  weightlifters, cyclists, football and rugby players have to pass anti-doping tests before attending the competition.

@@

\subsections{Lawyer consultations}

@@

>>>>

\begin{abstract}
Lorem ipsum\ldots
\end{abstract}
\keywords{data privacy, privacy preserving, zk-SNARK, blockchain}

\section{Problem statement}
Service providers (SP) like: lawyers, laboratories, auditors, or banks, to provide services, require data that is often associated with user identity.

Providing personal information exposes users to privacy risk, i.e. potential loss of control over personal information ~\cite{smith2011information}.

Such user information can be used then for commercial gains. For example, by reselling it to marketers, other businesses or even cybercriminals. Which in turn can lead to profiled advertisements, or cryminal activities like identity theft or illegal tracking and surveillance ~\cite{}

The guarantee of the privacy of the data is based on a trust assumptions and security of IT systems. However, most of the service providers don't need the information of user identity for other reasons than payment, communication, or logistics.

It would be desirable if the user could keep its identity private, while service provider still provide its services. This could lead to reduced trust that users have to put on SP and less responsibility borne by SP.

In this paper we propose a protocol for anonymous provision of services via blockchain and cryptography techniques. Specificaly, we use
\begin{enumerate}
    \item \textbf{confidential blockchain} to process payment for a service without revealing a user's identity.
    \item \textbf{zero-knowledge proofs} — to proof the payment for the service without revealing the payment itself.
    \item \textbf{encryption scheme and blockchain} — to asynchronously deliver the results of the made service back to the user.
\end{enumerate}

@@

\section{Applications}
\subsection{Anonymous clinical tests}
Bodybuilders, athletes,  weightlifters, cyclists, football and rugby players have to pass anti-doping tests before attending the competition.

@@

\subsection{Anonymous lawyer consultations}

@@

\subsection{Anonymous financial trustworthiness evaluation}

Evaluating financial trustworthiness is required when user want to, for example issue a credit card, take loan for a home, or rent a car. 
As defined in~\cite{lin2021efficient}, such a system consist of three parties: (i) users, (ii) credit bureaus, and (iii) creditors. Users willing to take a credit, have to provide to the credit bureaus, their financial activities like: new account creation, account balance, credit card utilization, credit inquires, and payment history. Such information are then submitted to creditors to compute the user's credit score.
